---
title: "Stable_DESeq-contrasts_SymC1"
author: "Mike Connelly"
date: "10/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DESeq2)
```
```{r}
resultsNames(dds)
```

##Results contrasts between individual treatments and control samples

### Antibiotics vs. Control
```{r}
res_anti_ctrl <- results(dds, contrast = c("treatment", "Antibiotics", "control"))
res_anti_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti_ctrl$IDGeneInfo <- as.character(res_anti_ctrl$IDGeneInfo)
ressig_anti_ctrl <- subset(res_anti_ctrl, padj<0.1 & abs(log2FoldChange)> 1)
ressig_anti_ctrl_up <- subset(res_anti_ctrl, padj<0.1 & log2FoldChange> 1)
ressig_anti_ctrl_dn <- subset(res_anti_ctrl, padj<0.1 & log2FoldChange< -1)
write.csv(as.data.frame(ressig_anti_ctrl[order(ressig_anti_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti_ctrl.csv")
write.csv(as.data.frame(ressig_anti_ctrl_up[order(ressig_anti_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti_ctrl_dn[order(ressig_anti_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti_ctrl_dn.csv")
colnames(res_anti_ctrl)
summary(res_anti_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti_ctrl_dn_ID.txt-e
```

### LPS vs. Control
```{r}
res_LPS_ctrl <- results(dds, contrast = c("treatment", "LPS", "control"))
res_LPS_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_LPS_ctrl$IDGeneInfo <- as.character(res_LPS_ctrl$IDGeneInfo)
ressig_LPS_ctrl <- subset(res_LPS_ctrl, padj<0.1 & abs(log2FoldChange)> 1)
ressig_LPS_ctrl_up <- subset(res_LPS_ctrl, padj<0.1 & log2FoldChange> 1)
ressig_LPS_ctrl_dn <- subset(res_LPS_ctrl, padj<0.1 & log2FoldChange< -1)
write.csv(as.data.frame(ressig_LPS_ctrl[order(ressig_LPS_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_LPS_ctrl.csv")
write.csv(as.data.frame(ressig_LPS_ctrl_up[order(ressig_LPS_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_LPS_ctrl_up.csv")
write.csv(as.data.frame(ressig_LPS_ctrl_dn[order(ressig_LPS_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_LPS_ctrl_dn.csv")
colnames(res_LPS_ctrl)
summary(res_LPS_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_LPS_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_LPS_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_LPS_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_LPS_ctrl_dn_ID.txt-e
```

### Heat vs. Control
```{r}
res_heat_ctrl <- results(dds, contrast = c("Treatment", "Heat", "control"))
#res_heat_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
#res_heat_ctrl$IDGeneInfo <- as.character(res_heat_ctrl$IDGeneInfo)
ressig_heat_ctrl <- subset(res_heat_ctrl, padj<0.1 & abs(log2FoldChange)> 1)
ressig_heat_ctrl_up <- subset(res_heat_ctrl, padj<0.1 & log2FoldChange> 1)
ressig_heat_ctrl_dn <- subset(res_heat_ctrl, padj<0.1 & log2FoldChange< -1)
write.csv(as.data.frame(ressig_heat_ctrl[order(ressig_heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_heat_ctrl.csv")
write.csv(as.data.frame(ressig_heat_ctrl_up[order(ressig_heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_heat_ctrl_dn[order(ressig_heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_heat_ctrl_dn.csv")
colnames(res_heat_ctrl)
summary(res_heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_heat_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_heat_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_heat_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_heat_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat vs. Control
```{r}
res_anti.heat_ctrl <- results(dds, contrast = c("treatment", "Antibiotics+Heat", "control"))
res_anti.heat_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat_ctrl$IDGeneInfo <- as.character(res_anti.heat_ctrl$IDGeneInfo)
ressig_anti.heat_ctrl <- subset(res_anti.heat_ctrl, padj<0.1 & abs(log2FoldChange)> 1)
ressig_anti.heat_ctrl_up <- subset(res_anti.heat_ctrl, padj<0.1 & log2FoldChange> 1)
ressig_anti.heat_ctrl_dn <- subset(res_anti.heat_ctrl, padj<0.1 & log2FoldChange< -1)
write.csv(as.data.frame(ressig_anti.heat_ctrl[order(ressig_anti.heat_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti.heat_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_up[order(ressig_anti.heat_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti.heat_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat_ctrl_dn[order(ressig_anti.heat_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti.heat_ctrl_dn.csv")
colnames(res_anti.heat_ctrl)
summary(res_anti.heat_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti.heat_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti.heat_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti.heat_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat + LPS vs. Control
```{r}
res_anti.heat.LPS_ctrl <- results(dds, contrast = c("treatment", "Antibiotics+Heat+LPS", "control"))
res_anti.heat.LPS_ctrl$IDGeneInfo <- mcols(dds)$IDGeneInfo
res_anti.heat.LPS_ctrl$IDGeneInfo <- as.character(res_anti.heat.LPS_ctrl$IDGeneInfo)
ressig_anti.heat.LPS_ctrl <- subset(res_anti.heat.LPS_ctrl, padj<0.1 & abs(log2FoldChange)> 1)
ressig_anti.heat.LPS_ctrl_up <- subset(res_anti.heat.LPS_ctrl, padj<0.1 & log2FoldChange> 1)
ressig_anti.heat.LPS_ctrl_dn <- subset(res_anti.heat.LPS_ctrl, padj<0.1 & log2FoldChange< -1)
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl[order(ressig_anti.heat.LPS_ctrl$padj, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti.heat.LPS_ctrl.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl_up[order(ressig_anti.heat.LPS_ctrl_up$log2FoldChange, decreasing = TRUE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti.heat.LPS_ctrl_up.csv")
write.csv(as.data.frame(ressig_anti.heat.LPS_ctrl_dn[order(ressig_anti.heat.LPS_ctrl_dn$log2FoldChange, decreasing = FALSE),]), file = "~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti.heat.LPS_ctrl_dn.csv")
colnames(res_anti.heat.LPS_ctrl)
summary(res_anti.heat.LPS_ctrl)
```
```{bash}
awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/overall/res_anti.heat.LPS_ctrl.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/up/res_anti.heat.LPS_ctrl_up.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_up_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_up_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_up_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_up_ID.txt-e

awk -F "," '{print $1}' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/tables/down/res_anti.heat.LPS_ctrl_dn.csv > ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
sed -i '' 1d ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
sed -i -e 's/"//g' ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_dn_ID.txt
rm ~/computing/scripts/EAPSI.HW-WT-master/DESeqresults_SymC1/lists/res_anti.heat.LPS_ctrl_dn_ID.txt-e
```

### Antibiotics + Heat vs. Antibiotics


### Antibiotics + Heat vs. Heat


### Antibiotics + Heat + LPS vs. Antibiotics


### Antibiotics + Heat + LPS vs. Heat


### Antibiotics + Heat + LPS vs. LPS


### Antibiotics + Heat + LPS vs. Antibiotics + Heat


### Antibiotics vs. LPS

